|

### 2021-03-10 supplementary_information_science.Rmd
Update supplementary_information_science.Rmd

For regression models, standardized regression coefficients (or its variant) are perhaps the most common summary when comparing effect sizes of explanatory variables. These values are useful if they are directly interpretable. For example, in linear regression models without interactions and/or variable transformations, regression coefficients have direct interpretations as they represent additive effects. However, there are many cases where regression coefficients are difficult to interpret. In our case, we regressed the log-transformed species richness on explanatory variables, so regression coefficients do not have direct interpretations at the original scale of the response variable $y$ (i.e., species richness).

@@

```{=tex}
\begin{equation}
  \Delta_u = \frac{\int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta (E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta))~p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta)}
                  { \int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta~(u^{(2)} - u^{(1)})~ p(u^{u^{(1)}}|v)~p(u^{u^{(2)}}|v)~p(v)~p(\Theta) }
\end{equation}
```
However, directly using the above equation is impractical because estimating $p(u^{(1)}|v)$ and $p(u^{(2)}|v)$ from finite data points is challenging (especially when $v$ is continuous). Instead, we estimated $\Delta_u$ using the following equation proposed by Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:

@@

```{=tex}
\begin{equation}
w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\Omega_v^{-1}(v_i-v_j)}
\end{equation}
```
where $\Omega_v^{-1}$ is the inverse of the variance-covariance matrix of $v$.

@@

```{=tex}
\begin{equation}
  \hat \Delta_{u,s} = \frac{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}
                           {\sum_{i=1}^n \sum_{j=1}^n w_{ij}(10^{u_j} - 10^{u_i})sign(u_j - u_i)}
\end{equation}
```
We exponentiated $u_i$ and $u_j$ because we log-transformed watershed area and branching probability in the statistical model. Then

>>>>

For regression models, standardized regression coefficients (or its variant) are perhaps the most common summary when comparing effect sizes of explanatory variables. These values are useful if they are directly interpretable. For example, in linear regression models without interactions and variable transformations, regression coefficients have direct interpretations as they represent additive effects. However, there are many cases where regression coefficients are difficult to interpret. In our case, we regressed the log-transformed species richness on explanatory variables, so regression coefficients do not have direct interpretations at the original scale of the response variable $y$ (i.e., species richness).

@@

```{=tex}
\begin{equation}
  \Delta_u = \frac{\int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta (E(y|u^{(2)}, v, \Theta) - E(y|u^{(1)}, v, \Theta))~p(u^{(1)}|v)~p(u^{(2)}|v)~p(v)~p(\Theta)}
                  { \int\int_{u^{(2)}>u^{(1)}}du^{(1)}du^{(2)}\int dv \int d\Theta~(u^{(2)} - u^{(1)})~ p(u^{(1)}|v)~p(u^{(2)}|v)~p(v)~p(\Theta) }
\end{equation}
```
However, directly using the above equation is impractical because estimating $p(u^{(1)}|v)$ and $p(u^{(2)}|v)$ from finite data points is challenging (especially when $v$ is continuous). Instead, we estimated $\Delta_u$ using the following equation proposed by Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:

@@

```{=tex}
\begin{equation}
w(v_i, v_j) = \frac{1}{1 + (v_i - v_j)^T\Omega_v^{-1}(v_i-v_j)}
\end{equation}
```
where $\Omega_v^{-1}$ is the inverse of the variance-covariance matrix of $v$. The function gives the maximum weight for a pair of $u_i$ and $u_j$ if $v_i = v_j$ (note that $v=v_i$ when $u = u_i$) while giving a less weight as the Mahalanobis distance between $v_i$ and $v_j$ increases. This property makes sense because our goal is to approximate the probability of transition from $u_i$ to $u_j$ with a common $v$ (i.e., $v_i = v_j$).

@@

```{=tex}
\begin{equation}
  \hat \Delta_{u,s} = \frac{\sum_{i=1}^n \sum_{j=1}^n w_{ij}(E(y|u_j, v_i, \Theta_s) - E(y|u_i, v_i, \Theta_s))sign(u_j - u_i)}
                           {\sum_{i=1}^n \sum_{j=1}^n w_{ij}(10^{u_j} - 10^{u_i})sign(u_j - u_i)}
\end{equation}
```
We exponentiated $u_i$ and $u_j$ in the denominator because we log-transformed watershed area and branching probability in the statistical model. Then
